---
title: "Assessment 1.1"
author: "Jason Owen Jongsoo"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Rmarkdown ***editing***

R Markdown is a file format for making dynamic documents with R. 
An R Markdown document is written in markdown (an easy-to-write plain text format) and contains chunks of embedded R code.

This is a link to Rmarkdown Studio Basics.
[Rmarkdown Studio Basics](https://rmarkdown.rstudio.com/lesson-8.html)

```{r include=FALSE}
library(dplyr)
library(knitr)
library(tidyverse)
library(skimr)
library(janitor)
library(scales)
library(lubridate)
```

Task 7

```{r echo=FALSE }

fastfood<-read.csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')
head(fastfood, n = 10L)
kable(fastfood[1:10 , 1:5], "pipe")

```

Task 8

```{r echo=FALSE}

fastfood_1<-fastfood %>% filter(calories>1000)
kable(fastfood_1, "pipe")

```

Task 9

```{r echo=FALSE}

dont_eat_this<-fastfood %>% filter(total_fat>40 & total_carb>80)
kable(dont_eat_this, "pipe")

```

Task 10

```{r echo=FALSE}

kable(fastfood %>% filter(restaurant=="Mcdonalds"), "pipe")

```

Task 11

```{r echo=FALSE}

skim(fastfood)

```

Task 12

```{r echo=FALSE}

kable(count(fastfood %>% group_by(restaurant)), "pipe")

```

Task 13

```{r echo=FALSE}

kable(fastfood %>% group_by(restaurant) %>% summarise(mean(calories)), "pipe")

```

Task 14

```{r echo=FALSE}

fastfood<-fastfood %>% group_by(restaurant) %>% mutate(average_calories=mean(calories))

kable(fastfood, "pipe")

```

Task 15

I choose kable to show the table of fastfood data set and grouped by restaurant 
to make it simpler and easier to read. Then I summaries and sum the total_fat according
to each restaurant
```{r echo=FALSE}

kable(fastfood %>% group_by(restaurant) %>% summarise(sum(total_fat)), "pipe")

```

Task 16

```{r echo=FALSE}

fastfood<-fastfood %>% group_by(restaurant) %>% mutate(max_total_fat=max(total_fat))

kable(fastfood, "pipe")

```


Task 17

```{r echo=FALSE}

fastfood %>% filter(restaurant=="Mcdonalds") %>% ggplot(aes(sugar, protein)) + geom_point() + ggtitle("Mcdonalds")

```

















